### 2010-07-07 subarchitectures/visualization.sa/trunk/doc/v11n.tex
v11n: manual updated

\subsection{A Passive Display Client}

@@

\section{Interaction with the display server}

An active display client is needed when the component wants to present some UI
elements with which it can be configured. The client receives notifications and
requests related to these elements from the display server. To achieve this 
a few methods must be overridden in a class derived from the CDisplayClient:

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
   class VideoViewer : public ManagedComponent, public VideoClient
   {
   private:
   #ifdef FEAT_VISUALIZATION
     class CVvDisplayClient: public cogx::display::CDisplayClient
     {
       VideoViewer* pViewer;
     public:
       CVvDisplayClient() { pViewer = NULL; }
       void setClientData(VideoViewer* pVideoViewer) { pViewer = pVideoViewer; }
       void handleEvent(const Visualization::TEvent &event); /*override*/
       std::string getControlState(const std::string& ctrlId); /*override*/
     };
     cogx::display::CActiveDisplayClient<VideoViewer> m_display;
   #endif
   };
\end{Verbatim}

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
   #ifdef FEAT_VISUALIZATION
   void VideoViewer::CVvDisplayClient::handleGuiEvent(
         const Visualization::TEvent &event)
   {
     if (event.type == Visualization::evCheckBoxChange) {
       if (event.sourceId == "toggle.viewer.running") {
         bool newrcv = (event.data != "0");
         if (newrcv != receiving) {
           if(receiving) {
             videoServer->stopReceiveImages(getComponentID());
           }
           else {
             videoServer->startReceiveImages(getComponentID(), camIds, 0, 0);
           }
           receiving = !receiving;
         }
       }
     }
   }
   #endif
\end{Verbatim}

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
   #ifdef FEAT_VISUALIZATION
   std::string VideoViewer::getControlState(const std::string& ctrlId)
   {
     if (ctrlId == "toggle.viewer.running") {
       return receiving ? "2" : "0";
     }
     return "";
   }
   #endif
\end{Verbatim}

@@

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
   void setHtml(const std::string& id, const std::string& partId,
         const std::string& htmlData); 
   void setHtmlHead(const std::string& id, const std::string& partId,
         const std::string& htmlData); 
\end{Verbatim}

@@

@@

>>>>

\subsection{A Passive Display Client}\label{section:PassiveClient}

@@

@@

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
   void setHtml(const std::string& id, const std::string& partId,
         const std::string& htmlData); 
   void setHtmlHead(const std::string& id, const std::string& partId,
         const std::string& htmlData); 
   void setHtmlForm(const std::string& id, const std::string& partId,
         const std::string& htmlData); 
\end{Verbatim}

@@

For a more detailed description of HTML form chuks see section
\ref{section:HtmlForms}.

@@

\section{Interaction with the Display Server}

In section \ref{section:PassiveClient} we described a simple client that is
able to send data to the Display Server. The server also supports some simple
user interface interaction with remote components. A client component that
wants to interact with the Display Server and receive notifications about UI
events can do it through an active display client. We derive a class from
\code{"CDisplayClient"} and override a few methods:

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
   class VideoViewer : public ManagedComponent, public VideoClient
   {
   private:
   #ifdef FEAT_VISUALIZATION
     class CVvDisplayClient: public cogx::display::CDisplayClient
     {
       VideoViewer* pViewer;
     public:
       CVvDisplayClient() { pViewer = NULL; }
       void setClientData(VideoViewer* pVideoViewer) { pViewer = pVideoViewer; }
       void handleEvent(const Visualization::TEvent &event); /*override*/
       std::string getControlState(const std::string& ctrlId); /*override*/
     };
     CVvDisplayClient m_display;
   #endif
   };
\end{Verbatim}

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
   #ifdef FEAT_VISUALIZATION
   void VideoViewer::CVvDisplayClient::handleGuiEvent(
         const Visualization::TEvent &event)
   {
     if (event.type == Visualization::evCheckBoxChange) {
       if (event.sourceId == "toggle.viewer.running") {
         bool newrcv = (event.data != "0");
         if (newrcv != pViewer->receiving) {
           if(pViewer->receiving) {
             pViewer->videoServer->stopReceiveImages(getComponentID());
           }
           else {
             pViewer->videoServer->startReceiveImages(getComponentID(), camIds, 0, 0);
           }
           pViewer->receiving = !pViewer->receiving;
         }
       }
     }
   }
   #endif
\end{Verbatim}

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
   #ifdef FEAT_VISUALIZATION
   std::string VideoViewer::CVvDisplayClient::getControlState(const std::string& ctrlId)
   {
     if (ctrlId == "toggle.viewer.running") {
       return pViewer->receiving ? "2" : "0";
     }
     return "";
   }
   #endif
\end{Verbatim}

\subsection{Support for HTML forms}\label{section:HtmlForms}

The display server can present HTML forms and send data from a form to a client
when the form is submitted.

To add support for form processing in an active client we override the methods
\code{"handleForm"} and \code{"getFormData"}. We also add a convenience
function that will create the form and send it to the server:

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
#ifdef FEAT_VISUALIZATION
   class COrDisplayClient: public cogx::display::CDisplayClient
   {
      CObjectRecognizer* pRecognizer;
   public:
      void createForms();
      void handleForm(const std::string& id, const std::string& partId,
            const std::map<std::string, std::string>& fields); /*override*/
      bool getFormData(const std::string& id, const std::string& partId,
            std::map<std::string, std::string>& fields); /*override*/
   };
\end{Verbatim}

A form can be defined with standard HTML form elements but it must not be
enclosed in the \code{"<form>"} tag which is added by the Display Server.

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
   void CObjectRecognizer::COrDisplayClient::createForms()
   {
      std::ostringstream ss;
      ss << "Min score: <select name='minScore'>";
      for (float f = 0.7; f <= 1.0; f += 0.01) {
         ss << "<option>" << sfloat(f, 2) << "</option>";
      }
      ss << "</select>";
      ss << "<input type=\"submit\" name=\"submit\" value=\"Apply\"/>";
      setHtmlForm("Settings", "ObjectRecognizer", ss.str());
   }
   std::string sfloat(double f, int precision)
   {
      std::ostringstream out;
      out << std::fixed << std::setprecision(precision) << f;
      return out.str();
   }
\end{Verbatim}

The getter and the setter functions pass the form parameters in a dictionary.
If a HTML field supports multiple values (like a multivalue select field, a
group of check boxes or radio buttons), the values are stored as a delimited
string where the delimiter is the newline character \Verb|"\n"|.

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
   void CObjectRecognizer::COrDisplayClient::handleForm(
         const std::string& id, const std::string& partId,
         const std::map<std::string, std::string>& fields)
   {
      if (! pRecognizer) return;
      if (id != "Settings" || partId != "ObjectRecognizer") retrun;
      float f;
      typeof(fields.begin()) it;
      it = fields.find("minScore");
      if (it != fields.end()) {
         f = atof(it->second.c_str());
         if (f < 0.7) f = 0.7;
         if (f > 1.0) f = 1.0;
         pRecognizer->m_minScore = f;
      }
   }

   bool CObjectRecognizer::COrDisplayClient::getFormData(
         const std::string& id, const std::string& partId,
         std::map<std::string, std::string>& fields)
   {
      if (! pRecognizer) return false;
      if (id != "Settings" || partId != "ObjectRecognizer") retrun false;
      fields["minScore"] = sfloat(pRecognizer->m_minScore, 2);
      fields["maxAmbiguity"] = sfloat(pRecognizer->m_maxAmbiguity, 2);
      return true;
   }
\end{Verbatim}

A form can be shown in a separate view or as a part of an HTML page composed of
multiple chunks. When a page contains a form it is slower to display because
some javascript has to be evaluated every time the page is reloaded. Therfore
the forms should not be a part of a page that is changed frequently (eg. more
than once per second).
